---
title: "lab8"
author: "Lil Rascals"
date: "3/6/2019"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(data.table)
library(tidyverse)
```

```{r}

library(data.table)
library(tidyverse)

workout <- read_csv("week16_exercise.csv", sep = ";", 
                   header = T,
                   na.strings = c("NA", "","?"),
                   stringsAsFactors = FALSE)
workout <- workout[-c(53:364), ] %>% filter(exercise>27) %>% select(state, exercise) %>% arrange(desc(exercise))
workout
ggplot(data= workout)+
  geom_col(mapping = aes(x=state, y=exercise, fill = state))+
  coord_flip()

```
###Kelsey McKenna
My question is which states were the top states in terms of exercise. 
I found that Colorado then Idaho are the top states in terms of exercise. 
The graph shows all states above 27 in the exercise column. 

###Team Question
How much has tuition changed over ten years. This is an important question, because seeing how data changes and how much tuition is increasing is an important issue for students. Also, it is essential to see whether tuition is increasing a reasonable amount or not. 
```{r}
library(data.table)
library(tidyverse)

tuition <- read_csv("us_avg_tuition.csv")

tuition <- tuition %>% select(State,'2004-05', '2014-15')
tuition
ggplot(data=tuition)+



```

###Team Summary
Kelsey McKenna
I uploaded the data in the form of csv instead of an excell file. I used the filter, select, and arrange functions in order to help answer my specific question. The data was pretty tidy already. The only problem was it had too many useless columns including a column of data with work status which wasn't useful. I also used header= T, na.strings, and stringsasFactors in order to tidy it further. 

